Active Code Completion

### 2012-03-20 icse12/graphite-icse12.tex
Finished adding related work to icse12.

Several refinements and additions to the code completion menu have previously been suggested in the literature. These have focused on leveraging additional sources of information, such as databases of usage history \cite{robbes_how_2008}, examples extracted from code repositories \cite{bruch_learning_2009} and crowdsourced information \cite{mooty_calcite:_2010}, to increase the relevance and sophistication of the featured menu items. As with the standard form of code completion, many of these sources of data can also be utilized via external tools (e.g. Calcite \cite{mooty_calcite:_2010} uses information that could already be accessed using the Jadeite \cite{conf/vl/StylosFYM09} tool). Empirical evidence presented in these studies, however, indicates that directly integrating these kinds of tools directly into the editor environment can be more effective.

@@

In addition to the references provided in the introduction, some other concepts are related to active code completion.

\subsection{Active Libraries}
We named this technique {\it active code completion} because of its relation to the general concept of {\it active libraries} \cite{activelibraries}. Active libraries are libraries that contain program logic that is invoked at either compile-time or, here, design-time.

@@

Editing environments like Barista \cite{Ko06} has previously been developed that merge concepts from both conventional text based and structured editors. Barista allows developers to use alternative code representations. It differs from Graphite in that these representations are built directly into the editor (although adding new representations is possible), and that Barista requires the users to use its own model-view-controller based language, which is likely to be unfamiliar to many users. In future work, we hope to explore an extensible, keyboard-driven, code-generation based approach that leverages structured code representations to eliminate the difficulties associated with reinvocation and maintaining palette state described in this paper.

\subsection{Specific IDE Features}
There exist some IDE features that have been specifically designed for certain types. For example, CodeRush has a ``show color dialog'' \cite{CodeRush} which allows the developers to launch a color picker directly from the code editor. Resharper \cite{Resharper} also has a color assistance tool which previews the actual colors right beside the code completion menu items. However, these IDE specific features are hard-coded -- user-defined types cannot provide similar functionality. Recent versions of Visual Studio have started to explore user-defined palettes for widgets in the windowing system.

@@

% use section* for acknowledgement
\section*{Acknowledgment}

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

>>>>

Several refinements and additions to the code completion menu have previously been suggested in the literature. These have focused on leveraging additional sources of information, such as databases of usage history \cite{robbes_how_2008}\cite{HouPletcher2011}, inheritance information \cite{HouPletcher2011}, API-specific information \cite{HouPletcher2011}\cite{Lee+2008}, partial abbreviations \cite{Han+2009}, examples extracted from code repositories \cite{bruch_learning_2009}\cite{Brandt+2010} and crowdsourced information \cite{mooty_calcite:_2010}\cite{SnipMatch}, to increase the relevance and sophistication of the featured menu items. As with the standard form of code completion, many of these sources of data can also be utilized via external tools (e.g. Calcite \cite{mooty_calcite:_2010} uses information that could already be accessed using the Jadeite \cite{conf/vl/StylosFYM09} tool). Empirical evidence presented in these studies, however, indicates that directly integrating these kinds of tools directly into the editor environment can be more effective.

@@

\subsection{Active Libraries}
We named this technique {\it active code completion} because of its relation to the general concept of {\it active libraries} \cite{activelibraries}. Active libraries are libraries that contain program logic that is invoked at either compile-time or, here, design-time.

@@

Editing environments like Barista \cite{Ko06} and the RBA editor \cite{RBA} also merge concepts from both text-based and structured editors by allowing for alternative code representations within a relatively conventional layout. Barista provides the opportunity for rich type-specific interfaces, but it is an IDE generation framework, so new extensions require recompilation. The RBA editor focuses on code readability rather than new modes of interaction, but new registrations can be added relatively easily. Both tools use a custom domain-specific language, which is likely to be unfamiliar to many users.

In future work, we hope to explore an extensible, keyboard-driven, code-generation based approach that leverages structured code representations to eliminate the difficulties associated with reinvocation and maintaining palette state described in this paper.

\subsection{Specific IDE Features}
There exist some IDE features that have been specifically designed for certain types. For example, CodeRush \cite{CodeRush} and Resharper \cite{Resharper} have color dialogs that allow developers to launch a color picker directly from the code editor. IntelliJ IDEA has an inline regular expression palette, driven by its Intentions system, as well \cite{IntelliJRegexp}. However, these IDE specific features are hard-coded -- user-defined types cannot provide similar functionality. Recent versions of Visual Studio support user-defined palettes associated with specific fields, rather than classes, of user interface widgets \cite{VSWidgets}. These are shown only in the property pane when using the graphical window layout editor.

@@

% use section* for acknowledgement
\section*{Acknowledgment}
% Funding sources
% Class 
% PLAID group / Jonathan Aldrich
% Participants
% Anonymous reviewers
% UIUC people

fasdfahsdfjk asdf alsdfhjkasdfh alsdhkjfh asdkflahs dfkjahs djkfhkjadfjakshf kjhasjdf akskdjfha sdhfkja sdfhajksdfa hsdfkaj sdfhasdf ahdfkajsd fhasdjkfhjas dkfa dfkadfa
fasdfahsdfjk asdf alsdfhjkasdfh alsdhkjfh asdkflahs dfkjahs djkfhkjadfjak
% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}
